%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {AI Chatbot Development} % Job title
  {Net7 SRL} % Organization
  {Pisa, Italy} % Location
  {Feb. 2024 - Jun. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a recommendation system for E-RIHS utilizing the technique of Retrieval-Augmented Generation via Langchain.}
      \item {Provided various invocable AI models with the Langserve REST API.}
      \item {Data management via Elasticsearch vector database, for efficient data retrieval and storage.}
      \item {Separation of concerns via Docker containerization of microservices, ensuring scalability and maintainability.}
      \item {Created a simple user interface via Streamlit to facilitate the API testing procedure by developers.}
      \item {Conducted AI system validation resulting in 83\% of overall precision.}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
  {Operations Management Intern} % Job title
  {P.B.L. Performing Beyond Limits} % Organization
  {Rubbiano di Solignano, Italy} % Location
  {Jun. 2020 - Aug. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Managed orders for materials required for the production line, ensuring timely availability to meet production demands.}
      \item {Organized and maintained the warehouse, optimizing layout for efficient material flow and accessibility.}
      \item {Conducted regular inventory checks to monitor stock levels and prevent shortages or overstock situations.}
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {3D Modeling Intern} % Job title
  {P.B.L. Performing Beyond Limits} % Organization
  {Rubbiano di Solignano, Italy} % Location
  {Jun. 2019 - Jul. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Utilized SolidWorks for complex 3D modeling projects, creating detailed mechanical components.}
      \item {Generated precise 2D technical drawings with comprehensive measurements for physical manufacturing.}
      \item {Managed orders for the manufacturing facility, coordinating with suppliers to ensure timely procurement of materials as needed.}
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {Web Developer} % Job title
  {Bardiani Valvole SPA} % Organization
  {Fornovo di Taro, Italy} % Location
  {Nov. 2020 - Jun. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and deployed a full-stack web portal to optimize various sizes valves packaging and as a result improve shipping efficiency.}
      \item {Architected and implemented a database solution using PHP and MySQL.}
      \item {Built responsive front-end interfaces using HTML, CSS and JavaScript with Bootstrap framework.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Web Developer} % Job title
  {Autodromo Riccardo Paletti} % Organization
  {Varano dé Melegari, Italy} % Location
  {Nov. 2018 - May 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered a comprehensive event management system handling real-time racing events, vehicle tracking, and participant management.}
      \item {Developed a scalable frontend using HTML5, CSS3, and Bootstrap, ensuring responsive design across devices.}
      \item {Implemented complex data management solutions using JSON and JavaScript + jQuery.}
    \end{cvitems}
  }
%---------------------------------------------------------
  \cventry
  {Web Developer} % Job title
  {Università degli Studi di Parma} % Organization
  {Parma, Italy} % Location
  {Jan. 2019 - Jan. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and developed responsive web pages for the university's official website using Drupal CMS.}
      \item {Usage of HTML and CSS.}
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}
